\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-19 icse/framework.tex
Revised intro & overview

\section{Building entire system to evaluate code}

@@

 In specification, "Well-known intrinsics are built-in objects that are explicitly referenced by the algorithms".
 Abstract algorithm uses name like "\%name\%", which are alias for builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
 Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.

@@

 Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is different.
The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Non-terminal
\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some non-terminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer sub-component of AST.
 For Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

>>>>

\section{Building entire system to extract semantics}\label{sec:framework}

@@

 In specification, "Well-known intrinsics are built-in objects that are explicitly referenced by the algorithms".
 Abstract algorithm uses identifiers like "\%name\%" to point builtin objects. For example it refers builtin Array object as \( \code{\%Array\%} \) .
 Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.

@@

 Like method-like abstract operation, many AST objects have similar interface, but they have different algorithm.
The most frequent example is "Evaluation" algorithm of AST Values. Many non-terminal symbol have different algorithm with name "Evaluation", and
when specification requires "the result of evaluating \textit{variable}", then it should apply "Evaluation" of non-terminal symbol which matches to \textit{variable}.
It is assumed that \textit{variable} is a AST value. Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
Evaluation algorithm of \textit{CallExpression} : \textit{CallExpression} \textit{Arguments}, algorithm can uses \textit{CallExpression} or \textit{Arguments} to refer sub-component of AST.
 To support Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

### 2019-08-19 icse/overview.tex
Updated overview image

\section{Overview}
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{img/overview.png}
  \caption{Overall structure of \( \tool \): Automatic extraction of
IR-based semantics for ECMAScript}
  \label{fig:overview}
\vspace*{-1em}
\end{figure}

@@

To generate {\sf JavaScript Parser} from a given \( \bnfes \) grammar, we
construct \textsf{JS Parser Generator} in Scala.  It synthesizes a
JavaScript parser according to the given \( \bnfes \), and the
generated parser is defined with Scala parser combinators~\cite{scala-parser-combinators}.
Moreover, in order to parse \( \bnfes \) grammars correctly and
efficiently, we propose \textit{lookahead parsers}, which keep track
of lookaheads, sets of possible next tokens.  With lookahead parsers,
generated parsers become more readable and have one-to-one
mapping to their corresponding grammar productions.
For example, Figure~\ref{fig:array-literal}(b) shows the generated
parser for the \textit{ArrayLiteral} production in Figure~\ref{fig:array-literal}(a).
Each parser has the \( \code{List[Boolean] => LAParser[T]} \) type
because  each production in \( \bnfes \) is parametric with boolean values.
The \( \code{memo} \) is a memoization function for pairs of boolean
parameters and resulting parsers for performance optimization.
The lazy value \( \code{ArrayLiteral} \) corresponds to the
\textit{ArrayLiteral} production.  In the parser, each string literal
such as \( \code{"["} \) or \( \code{"]"} \) denotes a parser for a
terminal symbol.  The \( \code{opt} \) helper function creates
optional parsers.  The parametric non-terminal \textit{ElementList}
with arguments \textsf{Yield} and \textsf{Await} is represented as a
function call \( \code{ElementList(Yield, Await)} \).
The \( \code{\textasciitilde} \) operator combines two parsers
and the \( \code{\^{}\^{}} \) operator describes how to construct ASTs.
When the left-hand side of \( \code{\^{}\^{}} \) is matched, its
right-hand side shows a corresponding AST constructor, where each
constructor has a number denoting the order among right-hand sides.
For example, the \( \code{ArrayLiteral0} \) constructor corresponds to
the first right-hand side of the \textit{ArrayLiteral} production.

@@

%because we utilize tag information to discriminate different kinds of tokens.
To translate such abstract algorithms into representations that are
suitable for manipulation, we define \( \ires \), a specialized
intermediate representation for ECMAScript abstract algorithms.  Then,
we develop \textsf{Algorithm Compiler} in Scala using Scala parser
combinators again to convert given abstract algorithms to \( \ires \)
functions.  It also takes \textsf{Compile Rules} as another input,
which has two parts: parsing rules and mapping from each rule to its
corresponding \( \ires \) component.  They are \textit{manually} specified for
the ECMAScript specification; we explain them in detail in
Section~\ref{sec:compiler}.  Thus, each abstract algorithm is
converted into a function written in \( \ires \) via \textsf{Algorithm Compiler}.
For example, Figure~\ref{fig:to-primitive}(b) presents the generated
\( \ires \) function for the \textbf{ToPrimitive} abstract algorithm.
The \( \code{ToPrimitive} \) function takes two parameters:
\( \code{input} \) and \( \code{PreferredType} \).  The optional
\( \code{PreferredType} \) parameter in the abstract algorithm has
a special value \( \code{absent} \) in the generated \( \ires \) function.
Thus, we convert the condition of the 2-a step,
``If \textit{PreferredType} is not present,'' into the equality check
with \( \code{absent} \): \( \code{if (= PreferredType absent)} \).
In this paper, we omit assertions for presentation brevity; we believe
that they can be handled similarly.  Some specific keywords are
represented as string values.  For instance, ``hint Number'' and
``hint String'' are converted into \( \code{"Number"} \) and
\( \code{"String"} \), respectively.  In addition,
\textsf{Algorithm Compiler} modifies prefixes of symbols from
\( \code{@@} \) to \( \code{SYMBOL\_} \) and handles exceptions with
their corresponding intrinsic error objects.

>>>>

\section{Overview}
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{img/overview.png}
  \caption{Overall structure of \( \tool \): Automatic extraction of
IR-based semantics for ECMAScript}
  \label{fig:overview}
\vspace*{-1em}
\end{figure}

@@

To generate {\sf JavaScript Parser} from a given \( \bnfes \) grammar, we
construct \textsf{JS Parser Generator} in Scala.  It synthesizes a
JavaScript parser according to the given \( \bnfes \), and the
generated parser is defined with Scala parser combinators~\cite{scala-parser-combinators}.
Moreover, in order to parse \( \bnfes \) grammars correctly and
efficiently, we propose \textit{lookahead parsers}, which keep track
of lookaheads, sets of possible next tokens.  With lookahead parsers,
generated parsers become more readable and have one-to-one
mapping to their corresponding grammar productions.
For example, Figure~\ref{fig:array-literal}(b) shows the generated
parser for the \textit{ArrayLiteral} production in Figure~\ref{fig:array-literal}(a).
Each parser has the \( \code{List[Boolean] => LAParser[T]} \) type
because  each production in \( \bnfes \) is parametric with boolean values.
The \( \code{memo} \) is a memoization function for pairs of boolean
parameters and resulting parsers for performance optimization.
The lazy value \( \code{ArrayLiteral} \) corresponds to the
\textit{ArrayLiteral} production.  In the parser, each string literal
such as \( \code{"["} \) or \( \code{"]"} \) denotes a parser for a
terminal symbol.  The \( \code{opt} \) helper function creates
optional parsers.  The parametric non-terminal \textit{ElementList}
with arguments \textsf{Yield} and \textsf{Await} is represented as a
function call \( \code{ElementList(Yield, Await)} \).
The \( \code{\textasciitilde} \) operator combines two parsers
and the \( \code{\^{}\^{}} \) operator describes how to construct ASTs.
When the left-hand side of \( \code{\^{}\^{}} \) is matched, its
right-hand side shows a corresponding AST constructor, where each
constructor has a number denoting the order among alternatives.
For example, the \( \code{ArrayLiteral0} \) constructor corresponds to
the first alternative of the \textit{ArrayLiteral} production.

@@

%because we utilize tag information to discriminate different kinds of tokens.
To translate such abstract algorithms into representations that are
suitable for manipulation, we define \( \ires \), a specialized
intermediate representation for ECMAScript abstract algorithms.  Then,
we develop \textsf{Algorithm Compiler} in Scala using Scala parser
combinators again to convert given abstract algorithms to \( \ires \)
functions.  It also takes \textsf{Compile Rules} as another input,
which has two parts: parsing rules and conversion rules from each rule to its
corresponding \( \ires \) component.  They are \textit{manually} specified for
the ECMAScript specification; we explain them in detail in
Section~\ref{sec:compiler}.  Thus, each abstract algorithm is
converted into a function written in \( \ires \) via \textsf{Algorithm Compiler}.
For example, Figure~\ref{fig:to-primitive}(b) presents the generated
\( \ires \) function for the \textbf{ToPrimitive} abstract algorithm.
The \( \code{ToPrimitive} \) function takes two parameters:
\( \code{input} \) and \( \code{PreferredType} \).  The optional
\( \code{PreferredType} \) parameter in the abstract algorithm has
a special value \( \code{absent} \) in the generated \( \ires \) function.
Thus, we convert the condition of the 2-a step,
``If \textit{PreferredType} is not present,'' into the equality check
with \( \code{absent} \): \( \code{if (= PreferredType absent)} \).
In this paper, we omit assertions for presentation brevity; we believe
that they can be handled similarly.  Some specific keywords are
represented as string values.  For instance, ``hint Number'' and
``hint String'' are converted into \( \code{"Number"} \) and
\( \code{"String"} \), respectively.  In addition,
\textsf{Algorithm Compiler} modifies prefixes of symbols from
\( \code{@@} \) to \( \code{SYMBOL\_} \) and handles exceptions with
their corresponding intrinsic error objects.
